---
title: "Reproducible Research: Peer Assessment 1"
author: "Melissa Pearson"
date: "1/9/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading and preprocessing the data

Create data folder in working directory if it does not exist, then access and download the data into this folder
```{r}
if(!file.exists("data")){dir.create("data")}
zipurl <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
destzip <- "./data/activitydata.zip"
destfile <- "./data/activitydata"
download.file(url=zipurl, destfile=destzip, method='curl')
unzip(destzip,exdir=destfile)
```


Load R libraries for use
```{r}
library(dplyr)
```

Load the data from the local data file into a data frame to use, and convert to tibble
```{r}
fname <- "./data/activitydata/activity.csv"
activity <- read.csv(fname)
activity <- tbl_df(activity)
```

## What is mean total number of steps taken per day?



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
